\vspace{-1.1em}

\cvsection{Work Experience}

\vspace{-0.2em}

\begin{cventries}

  \cventry
    {Software Development Engineer II} % Job title
    {Amazon} % Organization
    {London} % Location
    {Apr. 2022 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Backend service development in Python, Java, and TypeScript.}
        \item {Web development in TypeScript using React.}
        \item {Infrastructure as code using AWS CDK in TypeScript.}
        \item {Designed, implemented, and maintained service infrastructure using AWS Lambda, CloudFront, DynamoDB, OpenSearch, SQS, CloudWatch, S3, Bedrock, Step Functions, Batch, ECS, RDS, etc.}
        \item {Designed and implemented a trigger and pipeline processing 10M+ events per day to power Prime Video push notifications to 50M+ customers per month.}
        \item {Led a team of four engineers on the frontend development of an internal Amazon Studios web application.}
        \item {Developed, deployed, and maintained Dockerized Python services running on GPU compute environments in AWS ECS.}
        \item {Developed and maintained a backend Python service interacting with LLMs via Bedrock for an internal generative AI tool.}
        \item {Led a team and was part of another team that won two internal Prime Video and Studios hackathons with 50+ participants.}
        \item {Monthly on-call duty, fixing systems in real time to maintain high availability.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer} % Job title
    {BX} % Organization
    {London} % Location
    {Jan. 2021 -- Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web development in TypeScript using the Next.js React framework.}
        \item {Native mobile app development in TypeScript using React Native.}
        \item {Developing a serverless backend using AWS Lambda, API Gateway, DynamoDB, etc.}
        \item {Deploying resources within AWS using the Pulumi infrastructure as code SDK.}
        \item {Creating and editing assets on the Algorand blockchain using the Algorand SDK.}
      \end{cvitems}
    }

  \cventry
    {Computer Architecture Intern} % Job title
    {University of Bristol} % Organization
    {Bristol} % Location
    {Jul. 2020 -- Oct. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Extended the University of Bristol's ARM processor simulator (\textit{SimEng}) to include a model of the memory hierarchy using the C++ SST library.}
      \end{cvitems}
    }

  \vspace{-0.2em}
  
  % \cventry
  %   {High Performance Computing Teaching Assistant} % Job title
  %   {} % Organization
  %   {} % Location
  %   {Sep. 2019 -- Dec. 2019} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Taught third year students taking the High Performance Computing unit. Helped students parallelise stencil codes using the MPI and OpenMP libraries to run on multiple nodes of the Blue Crystal Phase 4 supercomputer.}
  %     \end{cvitems}
  %   }

  % \cventry
  %   {Intern} % Job title
  %   {Advanced Computing Research Centre (ACRC)} % Organization
  %   {Bristol} % Location
  %   {Jun. 2019 -- Sep. 2019} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Optimised scientific codes written in Fortran and C for researchers at the University of Bristol.}
  %       \item {Ported these codes to the ARM based Isambard and Catalyst supercomputers in Bristol.}
  %       \item {Set up a CI system using Buildkite to automatically keep track of the number of R packages successfully ported to ARM.}
  %     \end{cvitems}
  %   }

\end{cventries}
